---
title: "Homework 5 Solutions"
author: Laura Gomez
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
library(tidyverse)
library(p8105.datasets)
library(dplyr)
require(gridExtra)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = 0.6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 2

Import and tidy the following data set:
```{r}
data_1 = read_csv("1da_data/con_01.csv")
```

```{r, error = TRUE}
path_df = 
  tibble(
  path = list.files("1da_data"),
  ) %>%
  mutate(
  path = str_c("1da_data/", path),
  data = map(path,read_csv)) %>%
  unnest() %>%
  separate(col = path, into = c("path_1","path_2"), sep = 9,  remove = T) %>%
  separate(col = path_2, into = c("path_3","path_4"), sep = 4,  remove = T) %>%
  separate(path_4, c("subject_ID","csv")) %>%
  select(-path_1,-csv) %>%
  rename(control_arm = path_3)
```


Make a spaghetti plot showing observations on each subject over time
```{r spaghetti_plot_df}
Subject_time_df = path_df %>%
  pivot_longer(week_1:week_8, names_to = "Time", values_to = "subject_values") %>%
  separate(col = Time, into = c("drop","Time"), sep = 5,  remove = T)  %>%
  select(-drop)

Subject_time_df %>%
  mutate(Time = as.numeric(Time)) %>%
  ggplot(aes(x = Time, y = subject_values, color = subject_ID)) + 
  geom_point() + geom_line() + 
  theme(legend.position = "bottom")
```

Analyze the differences between Control and Experimental groups:
```{r}
# for the control
control_plot = filter( Subject_time_df, control_arm == "con_") %>%
  mutate(Time = as.numeric(Time)) %>%
  ggplot(aes(x = Time, y = subject_values, color = subject_ID)) + 
  geom_point() + geom_line() + 
  theme(legend.position = "bottom") +
    labs(
    title = "Observations of subjects in the control arm over time ",
    x = "Time (weeks)",
    y = "Participant Data ")
 

control_plot

# for the experimental 
exp_plot = filter( Subject_time_df, control_arm == "exp_") %>%
  mutate(Time = as.numeric(Time)) %>%
  ggplot(aes(x = Time, y = subject_values, color = subject_ID)) + 
  geom_point() + geom_line() + 
  theme(legend.position = "bottom") +
  labs(
    title = "Observations of subjects in the experimental arm over time ",
    x = "Time (weeks)",
    y = "Participant Data ")
 
exp_plot


grid.arrange(control_plot, exp_plot, ncol = 2)
```
The major differences between the control and experimental groups are the observational values for the control group trend downward overall following week 6 compared to the values for the experimental group trend upward overall for the subjects. The overall range of values for the control group are 
## Problem 3
```{r}
sim_ttest = function(n,  mu = 0, sigma = 5){
  
  sim_data = tibble(
    x = rnorm(n = 30, mean = mu, sd = sigma)
   )
  
  ttest = t.test(sim_data, mu = 0, sd = 5)
  ttest[['p.value']]
  ttest[['estimate']]
  
  sim_results = tibble(
    pvalue = ttest[['p.value']],
    mean = ttest[['estimate']]
  )
  
}

output = vector("list",100)

#map(.x = (0:6), ~rerun(5000, sim_ttest(mu =.x)))

#sim_results = bind_rows(output)

#data = tibble( mu = c(0:6)) %>%
                 #mutate(output_lists = map(.x = mu, ~rerun(5000, sim_ttest(mu = .x))),
                        #estimate_dfs = map(output_lists, bind_rows)) %>%
  #select(-output_lists) %>%
  #unnest(estimate_dfs)

###μ=0  using α=0.05. Hint: to obtain the estimate and p-value, use broom::tidy to clean the output of t.test.
  
##Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ on the x axis. Describe the association between effect size and power.
#Make a plot showing the average estimate of μ̂  on the y axis and the true value of μ on the x axis. Make a second plot (or overlay on the first) the average estimate of μ̂  only in samples for which the null was rejected on the y axis and the true value of μ on the x axis. Is the sample average of μ̂  across tests for which the null is rejected approximately equal to the true value of μ? Why or why not?


```

